Every Author as First Author

### 2023-03-28 paper.tex
Separate real stuff from joke

An additional benefit of our solution is that long lists of names can be
written in far less space.  This property is especially helpful for conferences
and journals with a hard limit on the number of pages including the bibliography
(including many with a printed publication).  For example, the 274 authors of
the human genome project \cite{human-genome} would normally take almost half
a page to list:

@@

As a result, many papers that cite this paper do not even list the entire
author list in the bibliography, instead writing ``J. C. Venter et al.''
% example: https://www.nature.com/articles/s41586-022-04601-8
Our approach makes it easy to give the full author list \cite{human-genome},
giving credit to all authors without allocating that paper a disproportionate
amount of space in the bibliography.

>>>>

An additional benefit of our solution is that long lists of names can be
written in far less space, and roughly the same amount of space for each paper.
For example, the 274 authors of the human genome project \cite{human-genome}
would normally take almost half a page to list:

@@

As a result, many papers that cite this paper do not list the entire
author list even in the bibliography, instead writing ``J. C. Venter et al.''
% example: https://www.nature.com/articles/s41586-022-04601-8
Our approach makes it easy to give the full author list \cite{human-genome},
giving credit to all authors, but without allocating that paper a
disproportionate amount of space in the bibliography.
Thus we help achieve fairness between cited papers, not just between authors
on each paper.

The space-savings property is also helpful for conferences and journals
with a hard limit on the number of pages including the bibliography.
Such limits are common among printed publications.
For such publications, the space savings also translates to a cost savings
for the publisher, and a reduction in trees needed to make paper ---
a helpful step toward resolving the climate crisis.
